Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-19 doc/GMP2015/s01_introduction.tex
More references and citations.

\begin{figure*}\centering
% \begin{subfigure}{.31\linewidth}\centering
%   \includegraphics[width=\linewidth]{img/Axopodium_Mikrotubuli}
%   \caption{Cross section of a Heliozoa's psuedopod, formed by a spiral structure of microtubules.}
%   % https://de.wikipedia.org/wiki/Mikrotubulus#mediaviewer/File:Axopodium_Mikrotubuli.jpg
%   \label{fig:material_examples:microtubule}
% \end{subfigure}\hfill
% \begin{subfigure}{.31\linewidth}\centering
%   \includegraphics[width=\linewidth]{img/Transverse_Section_Of_Bone}
%   \caption{Cross section of an osteon (the fundamental unit of compact bone) exhibiting its hierarchical structure.}
%   % https://en.wikipedia.org/wiki/Osteon#mediaviewer/File:Transverse_Section_Of_Bone.png
%   \label{fig:material_examples:osteon}
% \end{subfigure}\hfill
\begin{subfigure}{.28\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Chlamydomonas_TEM_17}
  \caption{Cross section of the Chlamydomonas algae axoneme, a cilia composed of microtubules.}
  % https://en.wikipedia.org/wiki/Axoneme#mediaviewer/File:Chlamydomonas_TEM_17.jpg
  \label{fig:material_examples:microtubule}
\end{subfigure}\hfill
\begin{subfigure}{.40\linewidth}\centering
  \includegraphics[width=\linewidth]{img/ligten2}
  \caption{Cross section of a tendon displaying the hierarchical structure.}
  % http://www.umich.edu/~bme332/ch10ligten/ligten2.jpg
  \label{fig:material_examples:tendon}
\end{subfigure}\hfill
\begin{subfigure}{.30\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Rothemund-DNA-SierpinskiGasket}
  \caption{A DNA array exhibiting the Sierpinski triangle.}
  % https://en.wikipedia.org/wiki/DNA_nanotechnology#mediaviewer/File:Rothemund-DNA-SierpinskiGasket.jpg
  \label{fig:material_examples:sierpinski}
\end{subfigure}
\caption{}\label{fig:material_examples}
\end{figure*}

@@

    \item Crosslinked cellulose or collagen microfibril monolayers e.g., in cell-walls~\cite{CellWalls1}~\cite{CellWalls1}, as well as crosslinked actin filaments in the cytoskeleton matrix.

@@

    \item Silica bi-layers~\cite{silica_bilayers}, glass~\cite{sructure_of_2d_glass}, and
    materials that behave like assemblies of 2D particles under
    non-overlap constraints, i.e, like jammed disks on the plane~\cite{jammed_disks}
\end{enumerate}
%
In order to study structural and mechanical properties
of a material layer, it is natural to model a material layer as a solution or
realization of a geometric constraint system of appropriate types of geometric
primitives, under metric or algebraic constraints. Such 2D
\dfn{qusecs} (quasi-uniform or self-similar constraint systems, defined
formally in Section \ref{sec:prelim}) can be
used to understand or design material layers (their solutions) with
desired properties.
%
\subsection{Previous Work on Relevant 2D Geometric Constraint Systems}
We now briefly survey existing techniques for studying 2D
qusecs,  many of which are \dfn{bar-joint} systems
(Examples 1, 2 above, see Sections \ref{sec:prelim}, \ref{sec:DRP}, \ref{sec:recomb}),
\dfn{body-hyperpin} systems (Example 4,5, see Section
\ref{sec:bodypin}) or \dfn{pinned-line incidence} systems (Example
3, see Section \ref{sec:pinnedline}). The limitations of these
techniques directly motivate the contributions of this paper.

>>>>

\begin{figure*}\centering
% \begin{subfigure}{.31\linewidth}\centering
%   \includegraphics[width=\linewidth]{img/Axopodium_Mikrotubuli}
%   \caption{Cross section of a Heliozoa's psuedopod, formed by a spiral structure of microtubules.}
%   % https://de.wikipedia.org/wiki/Mikrotubulus#mediaviewer/File:Axopodium_Mikrotubuli.jpg
%   \label{fig:material_examples:microtubule}
% \end{subfigure}\hfill
% \begin{subfigure}{.31\linewidth}\centering
%   \includegraphics[width=\linewidth]{img/Transverse_Section_Of_Bone}
%   \caption{Cross section of an osteon (the fundamental unit of compact bone) exhibiting its hierarchical structure.}
%   % https://en.wikipedia.org/wiki/Osteon#mediaviewer/File:Transverse_Section_Of_Bone.png
%   \label{fig:material_examples:osteon}
% \end{subfigure}\hfill
\begin{subfigure}{.28\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Chlamydomonas_TEM_17}
  \caption{Cross section of the Chlamydomonas algae axoneme, a cilia composed of microtubules~\cite{wikimediacommons2007cilia}.}
  \label{fig:material_examples:microtubule}
\end{subfigure}\hfill
\begin{subfigure}{.40\linewidth}\centering
  \includegraphics[width=\linewidth]{img/ligten2}
  \caption{Cross section of a tendon displaying the hierarchical structure~\cite{lecture_biosolid_mechanics}.}
  \label{fig:material_examples:tendon}
\end{subfigure}\hfill
\begin{subfigure}{.30\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Rothemund-DNA-SierpinskiGasket}
  \caption{A DNA array exhibiting the Sierpinski triangle~\cite{wikimediacommons2007dna}.}
  \label{fig:material_examples:sierpinski}
\end{subfigure}
\caption{}\label{fig:material_examples}
\end{figure*}

@@

    \item Crosslinked cellulose or collagen microfibril monolayers e.g., in cell-walls~\cite{wikimediacommons2010afm}~\cite{wikimediacommons2007plant}, as well as crosslinked actin filaments in the cytoskeleton matrix. See Section \ref{sec:pinnedline}.

@@

    \item Silica bi-layers~\cite{silica_bilayers}, glass~\cite{sructure_of_2d_glass}, and
    materials that behave like assemblies of 2D particles under
    non-overlap constraints, i.e, like jammed disks on the plane~\cite{jammed_disks}. See Section \ref{sec:bodypin}.
\end{enumerate}
%
In order to study structural and mechanical properties
of a material layer, it is natural to model a material layer as a solution or
realization of a geometric constraint system of appropriate types of geometric
primitives, under metric or algebraic constraints. Such 2D
\dfn{qusecs} (quasi-uniform or self-similar constraint systems, defined
formally in Section \ref{sec:prelim}) can be
used to understand or design material layers (their solutions) with
desired properties.
%
\subsection{Previous Work on Relevant 2D Geometric Constraint Systems}
We now briefly survey existing techniques for studying 2D
qusecs,  many of which are \dfn{bar-joint} systems
(Examples 1, 2 above, see Sections \ref{sec:prelim}, \ref{sec:DRP}, \ref{sec:recomb}),
\dfn{body-hyperpin} systems (Example 4,5, see Section
\ref{sec:bodypin}) or \dfn{pinned-line incidence} systems (Example
3, see Section \ref{sec:pinnedline}). The limitations of these
techniques directly motivate the contributions of this paper.
